
Loads essentials. Run create_btc_prediction_data.Rmd to update bitcoin_history.RDA data.
```{r}
setwd("~/Desktop/Crypto_Analysis-master")
source("custom_functions.R")
source("cor_matrix.R")
load("bitcoin_history.RDA")  # named df
#btc_2018 = 
```

Finding a model for predicting duration of correction
```{r}
# Selecting variables to use
colnames(df)
df2 = df[,-c(1:11,17:20)]
df2 = na.omit(df2)
colnames(df2)
pairs(df2[c(1:length(df2))], lower.panel=panel.smooth, upper.panel=panel.cor)

fit = lm(log.days.ath.atl ~ . , df2)
step_fit <- stepAIC(fit, direction="both")
step_fit$anova

final.fit = lm(log.days.ath.atl ~ reg.ath.atl + log.days.oatl.ath + log.reg.ath.atl, df2)
summary(fit)
summary(final.fit)

```

Testing model for predicting duration of correction
```{r}
# Model Equation



fit1 = lm(log.days.ath.atl ~ reg.ath.atl + log.days.oatl.ath + log.reg.ath.atl,df)
summary(fit1)

# Observed vs. Predicted Plot
fit1.predict = predict(fit1,df,type="response")
df.predict.fit1 = cbind(df,fit1.predict)
ggscatter(df.predict.fit1, x = "fit1.predict", y= "log.days.ath.atl", add = "reg.line", conf.int = TRUE, cor.coef = TRUE, cor.method = "pearson") %>% ggpar(xlab = "Predicted", ylab= "Observed", title = "Observed vs. Predicted Duration of BTC Corrections (Log Transformed)")

# Residual Diagnostics
par(mfrow = c(2,2))
plot(fit1)

# Compare to another model
#grid.arrange(pred_plot1, pred_plot2, ncol=1)

#colnames(crash_history_df)
# Scatterplot matrix and correlation matrix
#pairs(crash_history_df[c(3,7,8,10,11)], lower.panel=panel.smooth, upper.panel=panel.cor)
```

Testing model for predicting % decrease of correction (difference in price from start to end of correction)
```{r}

```

Testing model for predicting when prices will return/recover to previous all time high
```{r}
# Need to edit btc_crash_dates.xlsx
```

Testing model for predicting when the next correction will happen
```{r}

```

Testing model for predicting % increase in prices from all time low to new all time high (start of next correction)
```{r}

```



