
Load essentials.
```{r}
setwd("~/Desktop/Crypto_Analysis-master")
source("custom_functions.R")

today = Sys.Date()
```

If you get an error loading the above, you must update this package. Press "YES" to restart R.
```{r}
install.packages("crypto")
library(crypto)
```


#### How to use comparison_chart function####
comparison_date:
    The specific reference date that you want for all other dates to compare to. "YYYY-MM-DD" format. 
    Use today to refer to today's date.
    
end_date:
    The furthest date in the time interval you want to compare with. "YYYY-MM-DD" format. 
    [DEFAULT]: today's date.

month_or_day:
    "day" = [DEFAULT] Looks at all the days between the start date and end date.
    "month" = Looks at all the months between the start date and end date

interval:
    Takes a number as the argument. The interval number of months or days the start to end date is divided by. 
    [DEFAULT] value is 1.

type:
    "marketcap" = [DEFAULT] sorts dataset by marketcap (descending).
    "percent" = sorts each column of dataset by the coin with the highest gain since that month.
    "name" = sorts dataset by coin name.
    "nopercent" = sorts dataset by marketcap (descending) without percent or name labels.

```{r}
comparison_chart(comparison_date="2017-01-01", month_or_day="month", interval=1, type="percent", topranks=50)
```




#################################################################################

#### How to use generate_comparison function####
comparison_date:
    The specific reference date that you want for all other dates to compare to. "YYYY-MM-DD" format. 
    Use today to refer to today's date.
    
end_date:
    The furthest date in the time interval you want to compare with. "YYYY-MM-DD" format. 
    [DEFAULT]: today's date.

filter_name: 
	Compare by selected coin names.
	Format: c("Bitcoin", "Ethereum") selects Bitcoin and Etereum.

filter_rank: 
	Compare by marketcap rank instead of name. 
	Format: c(1:5) selects top 5 coins in marketcap.

Creates comparison graph of price changes
```{r}
# Creates comparison graph of specific coins
comparison_graph(comparison_date="2018-02-06", filter_name = c("Ripple", "Stellar", "Cardano", "Ethereum", "Bitcoin"))
```

```{r}
# Creates comparison graph of top 5 marketcap rank coins
comparison_graph(comparison_date="2018-02-06", filter_rank = c(1:5))
```




