
Load essentials.
```{r}
setwd("~/Desktop/Crypto_Analysis-master/Supplemental")
source("custom_functions.R")
today = Sys.Date()-1
```

Predict when downtrend will end

ooath.date = date that second last downtrend started
ooatl.date = date that second last downtrend ended
oath.date = date that last downtrend started
oatl.date = date that last downtrend ended
ath.date = date that current downtrend started
atl.date = date of lowest price (or today's date)
```{r}
predict_downtrend(
ooath.date = "2018-03-04",
ooatl.date = "2018-04-06",
oath.date = "2018-05-05",
oatl.date = "2018-06-28",
ath.date = "2018-07-28",
atl.date="2018-08-15"
)
```

Predict when uptrend will end

ooath.date = date that third last downtrend started
ooatl.date = date that third last downtrend ended
oath.date = date that second downtrend started
oatl.date = date that second last downtrend ended
ath.date = date that last downtrend started
atl.date = date that last downtrend ended


```{r}
predict_uptrend(
ooath.date = "2018-01-07",
ooatl.date = "2018-01-17",
oath.date="2018-01-20",
oatl.date = "2018-02-06",
ath.date = "2018-03-04",
atl.date = "2018-04-06",
nath.date = "2018-04-20"
)
```


```{r}
predict_uptrend(
ooath.date="2018-01-18",
ooatl.date = "2018-02-06",
oath.date = "2018-03-04",
oatl.date = "2018-04-06",
ath.date = "2018-05-05",
atl.date = "2018-06-28",
nath.date = "2018-07-17"
)
```


```{r}
predict_uptrend(
ooath.date = "2018-03-04",
ooatl.date = "2018-04-06",
oath.date = "2018-05-05",
oatl.date = "2018-06-28",
ath.date = "2018-07-28",
atl.date="2018-08-15",
	ci.level=0.975
)
```

