
Loads essentials. Run create_btc_prediction_data.Rmd to update bitcoin_history.RDA data.
```{r}
setwd("~/Desktop/Crypto_Analysis-master/Supplemental")
source("custom_functions.R")
source("cor_matrix.R")
load("bitcoin_history.RDA")  # named df
```


Finding a model for predicting when downtrend will end
```{r}
colnames(df)
variables1 = c("pct.ooath.ooatl",   "pct.ooatl.oath",   "pct.oath.oatl"   , "pct.oatl.ath"  ,    "pct.ooath.oath"      ,    "pct.oath.ath"   ,    "pct.ooatl.oatl"   ,  "days.ooath.ooatl"   ,     "days.ooatl.oath"     ,    "days.oath.oatl"       ,   "days.oatl.ath"     ,    "days.ooath.oath"    ,     "days.oath.ath"        ,  "days.ooatl.oatl"     ,    "pct.day.ooath.ooatl"  ,   "pct.day.ooatl.oath"    ,  "pct.day.oath.oatl"   ,  "pct.day.oatl.ath"  ,"pct.day.ooath.oath"  ,  "pct.day.oath.ath"   ,    
     "pct.day.ooatl.oatl"  , "reg.ooath.ooatl"   ,      "reg.ooatl.oath"     ,   "reg.oath.oatl"   ,    "reg.oatl.ath"  ,     "reg.ooath.oath"     ,     "reg.oath.ath"    ,        "reg.ooatl.oatl"    ,       "bad.months"    ,          "ath.bull", "days.ath.atl")

log.variables1 = c(paste0("log.",variables1)[-c(29:31)],variables1[29:31] ,"log.days.ath.atl")


df2 = df %>% na.omit() %>% select(variables1,log.reg.ath.atl)
log.df2 = df %>% na.omit() %>% select(log.variables1,log.reg.ath.atl)

# for no reg.ath.atl, no logs
pairs(df2[c(1:10,32)],lower.panel=panel.smooth, upper.panel=panel.cor,diag.panel=panel.hist,cex.labels=1)
pairs(df2[c(11:20,32)],lower.panel=panel.smooth, upper.panel=panel.cor,diag.panel=panel.hist,cex.labels=1) 
pairs(df2[c(21:31,32)],lower.panel=panel.smooth, upper.panel=panel.cor,diag.panel=panel.hist,cex.labels=1) 

pairs(df2[which(colnames(df2) %in% c("pct.day.oath.ath", "reg.oath.ath", "ath.bull", "atl.bull","days.ath.atl"))    ],lower.panel=panel.smooth, upper.panel=panel.cor,diag.panel=panel.hist,cex.labels=1) 

 # for no reg.ath.atl, logs
pairs(log.df2[c(1:10,33)],lower.panel=panel.smooth, upper.panel=panel.cor,diag.panel=panel.hist,cex.labels=1)
pairs(log.df2[c(11:20,32)],lower.panel=panel.smooth, upper.panel=panel.cor,diag.panel=panel.hist,cex.labels=1) 
pairs(log.df2[c(21:31,32)],lower.panel=panel.smooth, upper.panel=panel.cor,diag.panel=panel.hist,cex.labels=1) 

pairs(log.df2[which(colnames(log.df2) %in% c("log.pct.oath.oatl", "log.pct.oatl.ath", "log.pct.oath.ath", "log.days.ooatl.oath", "log.pct.day.oath.ath", "ath.bull","atl.bull", "log.reg.ath.atl","log.days.ath.atl"))    ],lower.panel=panel.smooth, upper.panel=panel.cor,diag.panel=panel.hist,cex.labels=1) 
  
# with no log.reg.ath.atl
d.fit1 = lm(log.days.ath.atl ~ log.pct.oath.oatl + log.pct.oath.ath , log.df2)
d.fit2 = lm(log.days.ath.atl ~ log.pct.oatl.ath + log.days.ooath.ooatl + 
    log.days.ooatl.oath + log.days.oath.oatl + log.days.ooath.oath + 
    log.reg.oath.oatl + log.reg.oath.ath + bad.months,log.df2)

# with log.reg.ath.atl
d.fit3 = lm(log.days.ath.atl ~ log.pct.ooath.oath + log.pct.oath.ath + 
     log.reg.ooatl.oath + 
    ath.bull + log.reg.ath.atl + log.pct.ooatl.oatl,log.df2)

d.fit4 = lm(log.days.ath.atl ~ log.pct.oatl.ath + log.pct.ooath.oath + 
    log.pct.oath.ath + log.pct.ooatl.oatl +
    log.days.oath.oatl + log.days.oatl.ath + log.days.oath.ath + 
    log.reg.ooatl.oath + log.reg.oatl.ath + ath.bull + log.reg.ath.atl,log.df2)


d.fit5 = lm(log.days.ath.atl ~ log.pct.oatl.ath +  log.pct.ooath.oath  +
    log.pct.oath.ath  + log.pct.ooatl.oatl +
    log.days.oath.oatl + log.days.oatl.ath + log.days.oath.ath + 
    log.reg.ooatl.oath + log.reg.oatl.ath +I(log.reg.oatl.ath^2) + ath.bull + log.reg.ath.atl + I(log.reg.ath.atl^2),log.df2)

d.fit6 = lm(log.days.ath.atl ~ log.pct.ooath.oath + log.pct.oath.ath + I(log.pct.ooatl.oatl^2) + ath.bull + log.reg.ath.atl ,log.df2)


d.fit7 = lm(log.days.ath.atl ~ log.pct.oatl.ath + log.pct.ooath.oath + 
    ath.bull + log.reg.ath.atl + I(log.pct.oatl.ath^3) + 
    I(log.pct.ooath.oath^3) + I(log.pct.oath.ath^3) + I(log.pct.ooatl.oatl^3) + 
    I(log.days.oath.oatl^3) + I(log.reg.ooatl.oath^3) + 
    I(log.reg.oatl.ath^3) + I(log.reg.ath.atl^3),log.df2)

d.fit8 = lm(log.days.ath.atl ~ log.pct.oatl.ath + log.pct.ooath.oath + log.days.oath.oatl + 
    log.reg.oatl.ath + ath.bull + log.reg.ath.atl + I(log.pct.oatl.ath^3) + 
    I(log.pct.ooath.oath^3) + I(log.pct.oath.ath^3) + I(log.pct.ooatl.oatl^3) + 
    I(log.days.oath.oatl^3) + I(log.days.oath.ath^3) + I(log.reg.ooatl.oath^3) + 
    I(log.reg.oatl.ath^3) + I(log.reg.ath.atl^3),log.df2)




fit.all = lm(log.days.ath.atl ~  log.pct.ooath.ooatl   +  log.pct.ooatl.oath    +  log.pct.oath.oatl    +   log.pct.oatl.ath  
+log.pct.ooath.oath  +    log.pct.oath.ath    +    log.pct.ooatl.oatl  +    log.days.ooath.ooatl   
+ log.days.ooatl.oath +    log.days.oath.oatl  +    log.days.oatl.ath   +    log.days.ooath.oath    
+log.days.oath.ath     +  log.days.ooatl.oatl   +  log.pct.day.ooath.ooatl+ log.pct.day.ooatl.oath 
+log.pct.day.oath.oatl  + log.pct.day.oatl.ath   + log.pct.day.ooath.oath  +log.pct.day.oath.ath  
+log.pct.day.ooatl.oatl  +log.reg.ooath.ooatl    + log.reg.ooatl.oath     + log.reg.oath.oatl      
+log.reg.oatl.ath       + log.reg.ooath.oath     + log.reg.oath.ath       + log.reg.ooatl.oatl     
+bad.months             + ath.bull + log.reg.ath.atl,log.df2   )

fit.all2 = lm(log.days.ath.atl ~ log.pct.oatl.ath + log.pct.ooath.oath + 
    log.pct.oath.ath + log.pct.ooatl.oatl +
    log.days.oath.oatl + log.days.oatl.ath + log.days.oath.ath + 
    log.reg.ooatl.oath + log.reg.oatl.ath + ath.bull + log.reg.ath.atl+
	I(log.pct.oatl.ath^3) + I(log.pct.ooath.oath^3) + 
    I(log.pct.oath.ath^3) + I(log.pct.ooatl.oatl^3) +
    I(log.days.oath.oatl^3) + I(log.days.oatl.ath^3) + I(log.days.oath.ath^3) + 
    I(log.reg.ooatl.oath^3) + I(log.reg.oatl.ath^3) +  I(log.reg.ath.atl^3)	
		
		,log.df2)

step_fit <- stepAIC(fit.all2, direction="both")
step_fit$anova
stepwise(downtrend_model3, direction = "backward/forward", criterion = "BIC")
# Compare models
stats1 = as.data.frame(ldply(list(d.fit1,d.fit2,d.fit3,d.fit4,d.fit5,d.fit6,d.fit7,d.fit8), model_fit_stats)[,2:3])
stats1

# comparing predicted to actual difference
df.predicted.diff = cbind(data.frame(observed = exp(log.df2$log.days.ath.atl)),as.data.frame(exp(predict(d.fit4, log.df2, se.fit=T, type='response',interval = "conf",level=0.8)$fit))) %>% arrange(fit)  %>%
	mutate(diff = fit-observed, diff.L = lwr - observed, diff.U = upr - observed, abs_diff = abs(diff))

stats2.function = function(model){
df.predicted.diff = cbind(data.frame(observed = exp(log.df2$log.days.ath.atl)),as.data.frame(exp(predict(model, log.df2, se.fit=T, type='response',interval = "conf",level=0.8)$fit))) %>% arrange(fit)  %>%
	mutate(diff = fit-observed,abs_diff = abs(diff)) %>% 
	summarize(sum_squared_error = sum(diff^2),
		mean_error = mean(abs_diff),
		median_error = median(abs_diff)
		)
return(df.predicted.diff)
}

stats2 = as.data.frame(matrix(nrow = 8, ncol = 3))
colnames(stats2) = c("sum_squared_error","mean_error","median_error")
stats2[1,] = stats2.function(model=d.fit1)
stats2[2,] = stats2.function(model=d.fit2)
stats2[3,] = stats2.function(model=d.fit3)
stats2[4,] = stats2.function(model=d.fit4)
stats2[5,] = stats2.function(model=d.fit5)
stats2[6,] = stats2.function(model=d.fit6)
stats2[7,] = stats2.function(model=d.fit7)
stats2[8,] = stats2.function(model=d.fit8)

stats_model = cbind(stats1,stats2)

ggplot(df.predicted.diff, aes(x = fit, y = diff)) +
    geom_point(size = 3,color="blue",alpha=0.7) +
	geom_hline(aes(yintercept=0),color="springgreen4",linetype="dashed") +
	geom_hline(aes(yintercept=0),color="springgreen3",alpha=0.25,size=1) +
	#geom_hline(aes(yintercept=5),color="springgreen4",linetype="dotted") +
	#geom_hline(aes(yintercept=-5),color="springgreen4",linetype="dotted") +
	#geom_vline(aes(xintercept=30),color="springgreen4",linetype="dotted") +
    geom_errorbar(aes(ymax = diff.U, ymin = diff.L),color="red",alpha=0.5, width=0.2) +
	scale_x_continuous(name="Predicted Number of Days Downtrend Will Last", breaks=seq(0,100,5)) +
	scale_y_continuous(name="Difference in Days Between Prediction and Actual Downtrend Duration (Prediction - Actual)",breaks=seq(-100,100,5))+
    theme_economist() + scale_colour_economist() +
	ggtitle("Error of Linear Model Predicting BTC Downtrend Duration") 
	


# See errors better
ggplot(df.predicted.diff, aes(x = fit, y = abs_diff)) +
    geom_point(size = 3,color="blue",alpha=0.7) +
	stat_smooth(geom = 'area', method = 'loess', span = .4 ,alpha = 1/2, fill = "lightblue4") + 
	geom_hline(aes(yintercept=0),color="green4",linetype="dashed",size=1.2,alpha=0.75) +
	#geom_hline(aes(yintercept=0),color="springgreen3",alpha=0.25,size=25) +
	geom_hline(aes(yintercept=5),color="springgreen3",linetype="dashed",size=1.2,alpha=0.75) +
	geom_hline(aes(yintercept=10),color="indianred2",linetype="dashed",size=1.2,alpha=0.75) +
	#geom_hline(aes(yintercept=-5),color="springgreen4",linetype="dotted") +
	#geom_vline(aes(xintercept=30),color="springgreen4",linetype="dotted") +
    #geom_errorbar(aes(ymax = diff.U, ymin = diff.L),color="red",alpha=0.5, width=1) +
	scale_x_continuous(name="Predicted Number of Days Downtrend Will Last", breaks=seq(0,100,5))+
	scale_y_continuous(name="Difference in Days Between Prediction and Actual Downtrend",breaks=seq(-100,100,5))+
    theme_economist() + scale_colour_economist() +
	ggtitle("Error of Linear Model Predicting BTC Downtrend Duration")



sjt.lm(downtrend_model2)

save(d.fit1,file="models/d.fit1.Rda")
save(d.fit2,file="models/d.fit2.Rda")
save(d.fit3,file="models/d.fit3.Rda")
save(d.fit4,file="models/d.fit4.Rda")
save(d.fit5,file="models/d.fit5.Rda")
save(d.fit6,file="models/d.fit6.Rda")
save(d.fit7,file="models/d.fit7.Rda")
save(d.fit8,file="models/d.fit8.Rda")
save(stats_model,file="models/stats_model.Rda")





```



Finding a model for predicting when downtrend will end without reg.ath.atl
```{r}
df2 = df


df2 = na.omit(df2)	
n= nrow(df2)
df2 = df2[-c(n,n-1),]

# all variables 
fit0 = lm(log.pct.ath.atl ~ pct.ooath.ooatl + pct.ooatl.oath  +   pct.oath.oatl  + pct.oatl.ath  +  
    pct.ooath.oath   +   pct.oath.ath   +      
 pct.ooatl.oatl  +   days.ooath.ooatl  +  days.ooatl.oath  +  
 days.oath.oatl  +   days.oatl.ath   +    days.ooath.oath  +  
 days.oath.ath   +   days.ooatl.oatl     +
 reg.ooath.ooatl  +   reg.ooatl.oath   +   reg.oath.oatl   +   
 reg.oatl.ath    +     reg.ooath.oath   +   reg.oath.ath   +    
  reg.ooatl.oatl + bad.months   +      
 ath.bull,df2)


# all logged variables
fit00 = lm(log.days.ath.atl ~	log.pct.ooath.ooatl +     log.pct.ooatl.oath  +    log.pct.oath.oatl +      log.pct.oatl.ath    +
    log.pct.ooath.oath   +   log.pct.oath.ath    +     
 log.pct.ooatl.oatl  +   log.days.ooath.ooatl +   log.days.ooatl.oath    +
 log.days.oath.oatl  +    log.days.oatl.ath     +      log.days.ooath.oath   + 
 log.days.oath.ath   +    log.days.ooatl.oatl    + 
 log.reg.ooath.ooatl   +  log.reg.ooatl.oath   +   log.reg.oath.oatl    +  
 log.reg.oatl.ath    +     log.reg.ooath.oath   +   log.reg.oath.ath   +    
  log.reg.ooatl.oatl,df3 )


fit000 = lm(log.pct.ath.atl ~	log.pct.ooath.ooatl +     log.pct.ooatl.oath  +    log.pct.oath.oatl +      log.pct.oatl.ath    +
    log.pct.ooath.oath   +   log.pct.oath.ath    +     
 log.pct.ooatl.oatl  +   log.days.ooath.ooatl +   log.days.ooatl.oath    +
 log.days.oath.oatl  +    log.days.oatl.ath     +      log.days.ooath.oath   + 
 log.days.oath.ath   +    log.days.ooatl.oatl    + 
		log.pct.day.ooath.ooatl +   log.pct.day.ooatl.oath    +
 log.pct.day.oath.oatl  +    log.pct.day.oatl.ath     +      log.pct.day.ooath.oath   + 
 log.pct.day.oath.ath   +    log.pct.day.ooatl.oatl    + 
 log.reg.ooath.ooatl   +  log.reg.ooatl.oath   +   log.reg.oath.oatl    +  
 log.reg.oatl.ath    +     log.reg.ooath.oath   +   log.reg.oath.ath   +    
  log.reg.ooatl.oatl + log.reg.ath.atl,df2 )

# keep: log.pct.oath.oatl     log.pct.oatl.ath    log.reg.oath.ath 


# with reg.ath.atl
fit1 = lm(log.pct.ath.atl ~ log.pct.oatl.ath + log.pct.ooath.oath + log.pct.ooatl.oatl + 
    log.days.oatl.ath + log.days.ooath.oath + log.days.oath.ath + 
    log.reg.oatl.ath,df2)


fit2 = lm(log.pct.ath.atl ~ pct.ooath.ooatl + pct.ooatl.oath + pct.ooath.oath + 
    days.oatl.ath + reg.ooath.ooatl + reg.ooatl.oatl + ath.bull,df2)


fit = lm(log.days.ath.atl ~ log.reg.ath.atl,df2)



summary(fit2)

pairs(df2[c(1:length(df2))], lower.panel=panel.smooth, upper.panel=panel.cor)



summary(fit7)
step_fit <- stepAIC(fit0, direction="both")
step_fit$anova
stepwise(fit6, direction = "backward/forward", criterion = "BIC")
ldply(list(fit1, fit2,fit3,fit4), model_fit_stats)


save(d.fit1,file="models/d.fit1.Rda")
save(d.fit2,file="models/d.fit2.Rda")
save(d.fit3,file="models/d.fit3.Rda")
save(d.fit4,file="models/d.fit4.Rda")
save(d.fit5,file="models/d.fit5.Rda")

```














Finding a model for predicting when the next correction will start
```{r}
colnames(df)
df3 = df[,c(7,9,11:22,24:34)]
df3 = na.omit(df3)
sapply(df3,class)
#df3 = df3[-12,]
#fit = lm(log.days.atl.nath ~ ., df3)
#step_fit <- stepAIC(fit5, direction="backward")
#step_fit$anova
# all variables 
fit0 = lm(log.pct.ath.atl ~ pct.ooath.ooatl + pct.ooatl.oath  +   pct.oath.oatl  + pct.oatl.ath  +  
    pct.ooath.oath   +   pct.oath.ath   +      
 pct.ooatl.oatl  +   days.ooath.ooatl  +  days.ooatl.oath  +  
 days.oath.oatl  +   days.oatl.ath   +    days.ooath.oath  +  
 days.oath.ath   +   days.ooatl.oatl     +
 reg.ooath.ooatl  +   reg.ooatl.oath   +   reg.oath.oatl   +   
 reg.oatl.ath    +     reg.ooath.oath   +   reg.oath.ath   +    
  reg.ooatl.oatl + bad.months   +      
 ath.bull,df2)


# all logged variables
fit00 = lm(log.days.ath.atl ~	log.pct.ooath.ooatl +     log.pct.ooatl.oath  +    log.pct.oath.oatl +      log.pct.oatl.ath    +
    log.pct.ooath.oath   +   log.pct.oath.ath    +     
 log.pct.ooatl.oatl  +   log.days.ooath.ooatl +   log.days.ooatl.oath    +
 log.days.oath.oatl  +    log.days.oatl.ath     +      log.days.ooath.oath   + 
 log.days.oath.ath   +    log.days.ooatl.oatl    + 
 log.reg.ooath.ooatl   +  log.reg.ooatl.oath   +   log.reg.oath.oatl    +  
 log.reg.oatl.ath    +     log.reg.ooath.oath   +   log.reg.oath.ath   +    
  log.reg.ooatl.oatl,df3 )


fit000 = lm(log.pct.ath.atl ~	log.pct.ooath.ooatl +     log.pct.ooatl.oath  +    log.pct.oath.oatl +      log.pct.oatl.ath    +
    log.pct.ooath.oath   +   log.pct.oath.ath    +     
 log.pct.ooatl.oatl  +   log.days.ooath.ooatl +   log.days.ooatl.oath    +
 log.days.oath.oatl  +    log.days.oatl.ath     +      log.days.ooath.oath   + 
 log.days.oath.ath   +    log.days.ooatl.oatl    + 
		log.pct.day.ooath.ooatl +   log.pct.day.ooatl.oath    +
 log.pct.day.oath.oatl  +    log.pct.day.oatl.ath     +      log.pct.day.ooath.oath   + 
 log.pct.day.oath.ath   +    log.pct.day.ooatl.oatl    + 
 log.reg.ooath.ooatl   +  log.reg.ooatl.oath   +   log.reg.oath.oatl    +  
 log.reg.oatl.ath    +     log.reg.ooath.oath   +   log.reg.oath.ath   +    
  log.reg.ooatl.oatl + log.reg.ath.atl,df2 )





uptrend_model = lm(log.days.atl.nath ~ pct.ath.atl + pct.day.oath.oatl + reg.atl.nath + 
    log.days.oatl.ath + log.days.oath.oatl + 
    I(days.oath.oatl^2) + I(reg.ath.atl^2) + I(days.oath.oatl^3) + 
    I(log.pct.ath.atl^3) + season + 
    log.days.oath.oatl:season + log.reg.atl.nath:season + I(log.reg.atl.nath^3):bull + 
    pct.day.oath.oatl:bull + reg.atl.nath:bull + log.days.oatl.ath:bull + 
    log.reg.atl.nath:bull + season:bull,df3)

summary(fit1)
step_fit <- stepAIC(fit0, direction="both")
step_fit$anova
stepwise(fit6, direction = "backward/forward", criterion = "BIC")
ldply(list(fit1, fit2,fit3,fit4), model_fit_stats)

# Comparing fits
#sjt.lm(fit2)
#summary(fit2)
#summary(fit5)


df.predicted.diff = cbind(data.frame(observed = exp(df3[,"log.days.atl.nath"]),as.data.frame(exp(predict(uptrend_model, df3, se.fit=T, type='response',interval = "conf",level=0.68)$fit)))) %>% arrange(fit) %>% 
	mutate(diff = fit-observed) %>% mutate(diff.L = lwr - observed) %>% mutate(diff.U = upr - observed) %>% mutate(abs_diff = abs(diff))

ggplot(df.predicted.diff, aes(x = fit, y = diff)) +
    geom_point(size = 3,color="blue",alpha=0.7) +
	geom_hline(aes(yintercept=0),color="springgreen4",linetype="dashed") +
	geom_hline(aes(yintercept=0),color="springgreen3",alpha=0.25,size=12) +
	geom_hline(aes(yintercept=5),color="springgreen4",linetype="dotted") +
	geom_hline(aes(yintercept=-5),color="springgreen4",linetype="dotted") +
    geom_errorbar(aes(ymax = diff.U, ymin = diff.L),color="red",alpha=0.5, width=1) +
	scale_x_continuous(name="Predicted Number of Days Uptrend Will Last", breaks=seq(0,5000,5))+
	scale_y_continuous(name="Difference in Days Between Prediction and Actual Correction Duration (Prediction - Actual)",breaks=seq(-100,100,5))+
    theme_economist() + scale_colour_economist() +
	#geom_smooth(method="loess", fill="orange", color = "orange", alpha = 0.2, size=0.5,span=0.5) +
	#geom_smooth(method="lm", fill="yellow", color = "yellow", alpha = 0.2, size=0.5) +
	ggtitle("Error of Linear Model Predicting BTC Uptrend Duration")


ggplot(df.predicted.diff, aes(x = fit, y = abs_diff)) +
    geom_point(size = 3,color="blue",alpha=0.7) +
	stat_smooth(geom = 'area', method = 'loess', span = .4 ,alpha = 0.3, fill = "lightblue4") + 
	geom_hline(aes(yintercept=0),color="green4",linetype="dashed",size=1.2,alpha=0.75) +
	#geom_hline(aes(yintercept=0),color="springgreen3",alpha=0.25,size=25) +
	geom_hline(aes(yintercept=5),color="springgreen3",linetype="dashed",size=1.2,alpha=0.75) +
	geom_hline(aes(yintercept=10),color="indianred2",linetype="dashed",size=1.2,alpha=0.75) +
	#geom_hline(aes(yintercept=-5),color="springgreen4",linetype="dotted") +
	#geom_vline(aes(xintercept=30),color="springgreen4",linetype="dotted") +
    #geom_errorbar(aes(ymax = diff.U, ymin = diff.L),color="red",alpha=0.5, width=1) +
	scale_x_continuous(name="Predicted Number of Days Uptrend Will Last", breaks=seq(0,1000,10))+
	scale_y_continuous(name="Difference in Days Between Predicted and Actual Uptrend Duration",breaks=seq(-100,100,5))+
    theme_economist() + scale_colour_economist() +
	ggtitle("Error of Linear Model Predicting BTC Uptrend Duration")


# Average difference when prediction is less than a month is 2.3 days
df.predicted.diff %>% filter(fit > 5 & fit <= 30) %>% mutate(abs_diff = abs(diff)) %>% dplyr::select(abs_diff) %>% colMeans()
# Average difference when predictino is between 1 to 2 months is 4.5 days
df.predicted.diff %>% filter(fit > 30 & fit <= 60) %>% mutate(abs_diff = abs(diff)) %>% dplyr::select(abs_diff) %>% colMeans()
# Average difference when predictino is more than 2 months is 20.4 days
df.predicted.diff %>% filter(fit > 60) %>% mutate(abs_diff = abs(diff)) %>% dplyr::select(abs_diff) %>% colMeans()

#save(uptrend_model,file="uptrend_model.Rda")
```



Finding a model for predicting duration of correction for predicting % decrease of correction (difference in price from start to end of correction)
```{r}

```

Finding a model for predicting when prices will return/recover to previous all time high
```{r}

```

Finding a model for predicting % increase in prices from all time low to new all time high (start of next correction)
```{r}

```



